Formalizing Stack Safety as a Security Property

### 2021-10-01 submission4/main.tex

%From the classic stack smashing attack to return oriented programming,
One of the most pernicious ways to attack the stack is by hijacking control flow.
Our stack safety properties do not assume that control flow follows a typical structure
of matching sets of calls and returns nested within one another.
Rather, they aim to capture what it means to protect data even in the presence of control-flow attacks.
Consider Figure~\ref{fig:controlflow}.
(Now we treat return addresses properly, but write them as line numbers, in the
form $\#n$.)
Function {\tt f} is called twice, at instructions 3 and 5; it should therefore return to instructions
4 and 6, respectively. But the first time, before returning, it stashes its
return pointer away, and the second time it returns to instruction 4 instead of 6; then it ends
up being called a third time, at which point it finally returns to instruction 6.

@@

\medskip
\paragraph*{Parameters Passed on the Stack}
%
Up to this point we have ignored function arguments, by assuming that they are placed
in registers (which are implicitly shared by all functions).
We now show how to implement two kinds of protected
sharing of stack contents: passing by value on the stack, and passing by
reference.
\ifspace
We first explore
some examples and then extend our formalization.
\fi

Example~\ref{fig:passingsimple} shows a sample trace of a program that passes
variables by reference. In this example, written in C++ notation,
{\tt f} takes a single argument by reference (the diagram displays it in magenta). The function
{\tt main} calls {\tt f}, passing a reference to {\tt x}, then clears {\tt x} and calls
{\tt f} again, passing a reference to {\tt y}.
We would expect that the first call to {\tt f} can modify
{\tt x}, but not the second. Unfortunately {\tt f} has hidden away our reference and modifies
{\tt x} in the second call. (Incidentally, this is perfectly compilable C++,
although its behavior is officially undefined.)

>>>>

%From the classic stack smashing attack to return oriented programming,
One of the most pernicious ways to attack the stack is by hijacking control flow.
Our stack safety properties do not assume that control flow follows a typical structure
of matching sets of calls and returns nested within one another.
Rather, they aim to capture what it means to protect data even in the presence of control-flow attacks.
Consider Figure~\ref{fig:controlflow}.
(Now we treat return addresses properly, but write them as line numbers, in the
form $\#n$.)
Function {\tt f} is called twice, at instructions 3 and 5; it should therefore return to instructions
4 and 6, respectively. But during the first call it stashes its
return pointer, and the second time it returns to instruction 4 instead of 6; it thus ends
up being called a third time before finally returning to instruction 6.

@@

\medskip
\paragraph*{Parameters Passed on the Stack}
%
Up to this point we have ignored function arguments, by assuming that they are placed
in registers (which are implicitly shared by all functions).
We now show how to implement two kinds of protected
sharing of stack contents: passing by value on the stack and passing by reference.
Here we give an example and high level discussion; the formalization can be found in Appendix \ref{app:argpass}.

Example~\ref{fig:passing} shows a sample trace of a program that passes
variables by reference. In this example, written in C++ notation,
{\tt f} takes a single argument by reference (the diagram displays it in magenta). The function
{\tt main} calls {\tt f}, passing a reference to {\tt x}, then clears {\tt x} and calls
{\tt f} again, passing a reference to {\tt y}.
We would expect that the first call to {\tt f} can modify
{\tt x}, but not the second. Unfortunately {\tt f} has hidden away our reference and modifies
{\tt x} in the second call. (Incidentally, this is perfectly compilable C++,
although its behavior is officially undefined.)
